Group 1: Tennis 

### 2019-12-10 Group1Prez.Rmd
Added to slides. Added more explaination on variables and flowchart about points.

@@

@@

@@

>>>>

## Project

- Project based off a paper by Paul K. Newton and Joseph B. Keller called Probability of Winning at Tennis 1. Theory and Data

- Paper discussed calculating the probability that one player, A, wins a tennis match against another player, B

- Based on other papers involving calculating the probability of winning a game in other racket sports the conclusion was made to treat points in tennis as  independent identically distributed (iid) random variables

- Although it is noted at points in tennis are not iid for most purposes this is not a bad assumption as the divergence from iid is small

  - This was supported by a statistical anaylsis of 4 years of Wimbledon data

@@

## Game of Tennis 
![](tennis-scoring.jpg){ width=85% }\

@@

- Where Probability A loses a rally given A served:$$q_A^R = 1-\frac{\text{Points Won On Serve}}{\text{Points Served}}$$

@@

Where:

- $$p_A^S=\text{Probabilty A wins a set given A served}$$

- $$p_B^S=\text{Probabilty B wins a set given B served}$$
